Puck Predictions: Unraveling the NHL Game Forecasting Riddle

### 2024-03-29 Latex/draft.tex
add dag picture

The computational complexity of Bayesian Network inference is high, with exact inference being an NP-hard problem TODO CITE. 
Using the python package pgmpy, we originally tried to fit a network with all 26 of our features, but our computational resources failed to fit this network.
Then, to get a baseline for our future predictions, we simply fitted the model with the base features of home goals, away goals, home shots, away shots, home blocked shots, and away blocked shots. 
These features were chosen as priors because of our opinion that they are the most important to the game, based upon our knowledge of hockey.

(Basic graph to test)

\begin{center}
    \begin{tikzpicture}[node distance={15mm}, thick, main/.style = {draw, circle}]
        \node[main] (1) {t r}; 
        \node[main] (2) [below left of=1] {t g};
        \node[main] (3) [below right of=1] {t s};
        \node[main] (4) [below right of=3] {t b};

        \draw[->] (1) -- (2);
        \draw[->] (1) -- (3);
        \draw[->] (1) to [out=15,in=90,looseness=1.5] (4);

@@

\begin{figure}[H]
    \centering
    \includegraphics[width=0.8\textwidth]{images/simulation_v_actual_dimred.png}
    \caption{PCA, t-SNE and UMAP performed on a dataset with final event counts for 1500 simulated and 1500 actual NHL games. This evidences that our simulation accurately emulates live NHL games}
    \label{fig:simulation_v_actual}
\end{figure}

>>>>

The computational complexity of Bayesian Network inference is high, with exact inference being an NP-hard problem TODO CITE. 
Using the python package pgmpy, we originally tried to fit a network with all 26 of our features, but our computational resources failed to fit this network.
Then, to get a baseline for our future predictions, we simply fitted the model with the base features of time remaining (tr), home goals (hg), away goals (ag), home shots (hs), away shots (as), home blocked shots (hbs), and away blocked shots (abs). 
These features were chosen as priors because of our opinion that they are the most important to the game, based upon our knowledge of hockey.

The conditional dependencies of the chosen network are shown in the DAG below:

\begin{center}
    \begin{tikzpicture}[node distance={15mm}, thick, main/.style = {draw, circle}]
        \node[main] (1) {tr}; 
        \node[main] (2) [below left of=1] {hs};
        \node[main] (3) [below right of=1] {as};
        \node[main] (4) [below right of=3] {hbs};
        \node[main] (5) [below left of=2] {abs};
        \node[main] (6) [below right of=5] {hg};
        \node[main] (7) [below left of=4] {ag};

        \draw[->] (1) -- (2);
        \draw[->] (1) -- (3);
        \draw[->] (3) -- (4);
        \draw[->] (2) -- (5);
        \draw[->] (5) -- (6);
        \draw[->] (4) -- (7);
        \draw[->] (3) -- (7);
        \draw[->] (2) -- (6);

@@

\begin{figure}[H]
    \centering
    \includegraphics[width=0.8\textwidth]{images/simulation_v_actual_dimred.png}
    \caption{PCA, t-SNE and UMAP performed on a dataset with final event counts for 1500 simulated and 1500 actual NHL games. The joined grouping demonstrates that our simulation accurately emulates live NHL games}
    \label{fig:simulation_v_actual}
\end{figure}
